Scalar on Function Regression

### 2022-01-06 Presentation/slides.tex
Removed Jakob ToDo Slides

	\begin{frame}{Theory}
		Jakob
		\begin{itemize}
			\item Random function represented as linear combination of basis functions $\checkmark$
			\item Just transform to multiple linear regression setting $\checkmark$
			\item You already know that from the beginning $\checkmark$
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Theory - FPCA}
		Jakob
		\begin{itemize}
			\item Let's assume you know the theory of PCA (pc from varcov matrix) $\checkmark$
			\item Introduce mean and covariance functions of random functions $\checkmark$
			\item There is another cool basis $\rightarrow$ Eigenbasis (Karhunen-Loeve Expansion) $\checkmark$
			\item Sample Analog! (create a basis from observations and use for basis regression) $\checkmark$
			\item Plot fpcs and approximation of function realization
		\end{itemize}
	\end{frame}

>>>>

	%\begin{frame}{Theory}
	%	Jakob
	%	\begin{itemize}
	%		\item Random function represented as linear combination of basis functions $\checkmark$
	%		\item Just transform to multiple linear regression setting $\checkmark$
	%		\item You already know that from the beginning $\checkmark$
	%	\end{itemize}
	%\end{frame}

@@

	%\begin{frame}{Theory - FPCA}
	%	Jakob
	%	\begin{itemize}
	%		\item Let's assume you know the theory of PCA (pc from varcov matrix) $\checkmark$
	%		\item Introduce mean and covariance functions of random functions $\checkmark$
	%		\item There is another cool basis $\rightarrow$ Eigenbasis (Karhunen-Loeve Expansion) $\checkmark$
	%		\item Sample Analog! (create a basis from observations and use for basis regression) $\checkmark$
	%		\item Plot fpcs and approximation of function realization
	%	\end{itemize}
	%\end{frame}
